---
title: "Shiny Application and Reproducible Pitch"
author: "Yuan Li"
date: '2022-07-19'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Introduction

This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.

2. Deploy the application on Rstudio's shiny server

3. Share the application link by pasting it into the provided text box

4. Share your server.R and ui.R code on github


## How to use the application

It is a simple application help to view the number of telephones in various regions of the world (in thousands). You can just simply selecting the region and the trend of number of telephones through years will shown to you. 
The regions are: North America, Europe, Asia, South America, Oceania, Africa, Central America.
The years are: 1951, 1956, 1957, 1958, 1959, 1960, 1961.

The application is running on [here](http://127.0.0.1:3339/)

To see theui.R, and Server.R Code, please visit my [github repository](https://github.com/YCherL/Course9-Developing-Data-Products)

##  WorldPhones Dataset

The data used in the app comes from the WorldPhones dataset. 

```{r echo=TRUE}
library(datasets)
data(WorldPhones)
summary(WorldPhones)
head(WorldPhones)

```


## Number of Telephones in Asia
```{r}
barplot(WorldPhones[,"Asia"]*1000, 
                main="Number of Telephones in Asia",
                ylab="Number of Telephones",
                xlab="Year", col = "#56B4E9", border = "#E69F00")
```










